Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-30 VMCAI-revised-version/final.tex
effectivity

By using the decidability of reachability and Theorem 3.11 in \cite{DBLP:journals/acta/ValkJ85}, we may prove that VASS are $\pred^*$-basis-effective. A more complete study of these properties will be done in the long version of this paper.

@@

%An equivalent formulation is : Does there exist $t \in S$ such that $s_0 \longrightarrow^{*} t$ and $s \leq t$ ?
With the $\pred$-basis-effective hypothesis, we obtain:
%
%			(Finkel and Schnoebelen, Abdulla and al., 
%
\begin{theorem}[Theorem 3.6, \cite{DBLP:journals/tcs/FinkelS01}, Theorem 4.1, \cite{DBLP:journals/iandc/AbdullaCJT00}]
 A finite basis of $ \pred^*(U)$ is computable for any $\pred$-basis-effective WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ and any upward-closed set $U \subseteq S$ given with its finite basis $B_U$. Hence coverability is decidable.
\end{theorem}

>>>>

By using the decidability of reachability and \cite[Theorem 3.11]{DBLP:journals/acta/ValkJ85}, we may prove that VASS are $\pred^*$-basis-effective. A more complete study of these properties will be done in the long version of this paper.

@@

%An equivalent formulation is : Does there exist $t \in S$ such that $s_0 \longrightarrow^{*} t$ and $s \leq t$ ?
With the $\pred$-basis-effective hypothesis, we obtain:
%
%			(Finkel and Schnoebelen, Abdulla and al., 
%
\begin{theorem}[Theorem 3.6, \cite{DBLP:journals/tcs/FinkelS01}, Theorem 4.1, \cite{DBLP:journals/iandc/AbdullaCJT00}]
 A finite basis of $ \pred^*(U)$ is computable for any $\pred$-basis-effective WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ and any upward-closed set $U \subseteq S$ given with its finite basis. Hence coverability is decidable.
\end{theorem}
